Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-11 manuscript/manuscript.tex
Minor changes in manuscript

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the gravity fields generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the exponential density defined on equation \ref{eq:density-exp} for different values of $b$. Each computation was performed on the big grid described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/Dexp-power-differences.pdf}
\caption{
    Differences between the Marussi tensor component $g_{zz}$ generated by the numerical model and the analytical solution for a thin spherical shell of 1km of thickness and the exponential density defined on equation \ref{eq:density-exp} for different values of $b$. Each computation was performed on the big grid described in Table \ref{tab:grids} and for different values of the distance-size ratio $D$. If the difference is less than 10$^{-1}\%$, we consider that the model has achieved an acceptable accuracy for the corresponding value of $D$.
}
\label{fig:D-exp-power}
\end{figure}
